outline!

### 2016-05-15 paper.tex
paper: corfu desc
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\subsection{Motivating Example: CORFU Log}

>>>>

\subsection{Motivating Example: CORFU}

The primary motivating example we will use in this paper is the CORFU
distributed shared-log designed to provide high-performance serialization
across a set of flash storage devices~\cite{balakrishnan:nsdi12}. The
shared-log is a powerful abstraction useful when building distributed systems
and applications, but common implementations such as Paxos or Raft funnel I/O
through a single node limiting the throughput of log
operations~\cite{lamport:tocs89}. The CORFU protocol addresses this limitation
by de-coupling log entry storage from log metadata, making use of a
centeralized, volatile, in-memory \emph{sequencer service} that assigns log
positions to clients that are appending to the log. Since the sequencer is
centeralized serialization is trivial, and the use of non-durable state allows
the sequencer service to operate at very high rates.

While a full description of the CORFU protocol is beyond the scope of this
paper, it is important to highlight the usage of application-specific flash
I/O interfaces in CORFU that are used to guarantee correctness during failure.
Each flash device in CORFU exposes a 64-bit write-once address space
consisting of the primary interfaces \emph{write(pos, data)} and
\emph{read(pos)}, as well as \emph{fill(pos)} and \emph{trim(pos)} that
invalidate and reclaim log entries, respectively. All I/O operations initiated
by clients are tagged with an \emph{epoch} value, and flash devices are
expected to reject client requests requests tagged with an old epoch value. To
facilitate recovery or handle system reconfiguration in CORFU, the storage
devices are also required to support a \emph{seal(epoch)} command that marks
the latest epoch and returns the maximum position written to that device. The
seal interface is used following the failure of a sequencer to calculate the
tail of the log that the sequencer should use to repopulate its in-memory
state.

why ceph and corfu?
